\documentclass{article}

\title{Image Based Lighting in Real-Time - Project Proposal}
\author{Jo\~{a}o Pedro Jorge \and Willem Frishert}
\date{18-02-2007}

\begin{document}
\maketitle

\section{Proposal}

We propose to implement a Real-Time approach of Image Based Lighting (like done by ATI for \textit{Rendering with Natural Light}) like described in \cite{bib:HDRBook}. For our base implementation the following features will be present:

\begin{itemize}
	\item Computations using HDR images
	\item Tone Mapping using a Global Operator (not chosen yet)
	\item Synthetic objects materials: basic diffuse and specular objects
	\item Background built using Cube Mapping
	\item User interactivity
\end{itemize}
Due to time constraints on this project the next features will be considered optional:
\begin{itemize}
	\item More complex BRDF's: Fresnel Reflection (Glass), Anisotropic Reflection 
(Metallic surfaces)
	\item Shadows
	\item Depth-Of-Field effect
	\item Lens Flare / Glare
	\item Motion Blur
	\item Camera / Object animation
	\item Multiscale Retinex Local Tone Mapping Algorithm
\end{itemize}

The scenario will comprise several simple synthetic objects being lit by information retrieved from lightprobes \cite{bib:HDRBook}. The implementation will be done in openGL 2.0 and GLSL Shading Language.
The starting references will be \cite{bib:FBOs, bib:HDRTM, bib:HDRTexturing, bib:RTIBL, bib:HDRBook}.

% ### BIBLIOGRAPHY ###
\begin{thebibliography}{99}

\bibitem{bib:HDRTexturing} Persson, E., 2005, HDR Texturing. In \textit{ATI SDK }.

\bibitem{bib:FBOs} Persson, E., 2005, Framebuffer Objects. In \textit{ATI SDK }.

\bibitem{bib:HDRBook} Reinhard, E., Ward, G., Pattanaik, S. and Debevec, P., 2006, High Dynamic Range Imaging, Acquisitio, Display and Image Based Lighting. The Morgan Kaufmann Series in Computer Graphics.

\bibitem{bib:HDRTM} Cohen, J., Tchou, C., Hawkins, T. and Debevec, P., 2001,Real-Time High Dynamic Range Texture Mapping. In {\it Proceedings of the 12th Eurographics Workshop on Rendering Techniques}, Springer-Verlag pp. 313-320.

\bibitem{bib:RTIBL} Unger, J., Wrenninge, M. and Ollila, M., 2003, Real-Time Image Based Lighting in Software using HDR Panoramas. In {\it Proceedings of the 1st international conference on Computer graphics and interactive techniques in Australasia and South East Asia}, ACM Press pp. 263-ff.



\end{thebibliography}




\end{document}
